Growth model analysis 3spp WB

### 2018-12-11 manuscriptAnalysis/MS_Analysis_3spp_WB.Rmd
sens analysis on gr instead of size

#data for running the simulation
simData <- list(
  nReps = 25,#100, #num of mcmc iterations to grab
  numInd = 500 , # number of individual to simulate
  nOccYOY = 3,
  nOccAdult = 7,
  riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear
  minSD = -2, #range and step for independent variable values in the sim
  maxSD = 2, 
  step = 1
)
simData$nOcc <- simData$nOccYOY + simData$nOccAdult
simData$indVarSeq = c(-1.5, -0.75, 0, 1.5) #seq(simData$minSD,simData$maxSD,simData$step)

stats3Spp <- anov <- elapsed <- lm <- relImp <- list()
spp <- c('bkt','bnt','ats')

@@

  startTime <- Sys.time()
  sizeStats <- sizeStats2 <- NULL
  #loop over conditions
  for(testRow in indVars$rowNum){
    sizeMat <- projectSizes(m,simData,testRow)

    sizeStats1 <- summarizeLens(sizeMat,testRow)
    sizeStats <- rbind(sizeStats,sizeStats1[[1]]) #means over individuals (grouped by iter, occ)
    sizeStats2 <- rbind(sizeStats2,sizeStats1[[2]]) #means by occ of means over individuals (grouped by occ)
  }
  endTime <- Sys.time()
  (elapsed[[speciesForProj]] <- endTime - startTime)

  stats3Spp[[speciesForProj]] <- list( sizeStats,sizeStats2 )

  lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt*bkt, data = sizeStats %>% filter(occ == (simData$nOcc)))

  relImp[[speciesForProj]] <- calc.relimp(lm[[speciesForProj]], type = c("lmg"), rela = TRUE)

  anov[[speciesForProj]] <- anova( lm[[speciesForProj]] )

@@

#projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
save( stats3Spp, lm, relImp, anov, elapsed, simData, file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))

# if not re-running the sim
# load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
# temporary while projOut is a list
# stats3Spp <- projOut[[1]]
# relImpData <- projOut[[3]]
# anovData <- projOut[[4]]
# simData <- projOut[[6]]
# spp <- c('bkt','bnt','ats')

# raw sim data figs
ggplot(stats3Spp[['bkt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0), aes(as.numeric(occ),lenMean)) +
  #geom_point(aes(color = factor(ats))) +
  #geom_smooth(aes(color = factor(temp), linetype = factor(flow)))+#(bnt + 2)/4 )) +
  geom_smooth()+#(bnt + 2)/4 )) +
  geom_smooth(color = 'green', data = stats3Spp[['bnt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0)) +
  facet_grid(temp ~ flow)

@@

# projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
load('D:/projects/linkedModels/data/out/projectionOut.RData')
stats3Spp <- projOut[[1]]
spp <- c('bkt','bnt','ats')
# scenarios
# Plot subsets of the simulations
#means for each iter
stats1 <- rbind(data.frame(stats3Spp[['bkt']][[1]]), 
                data.frame(stats3Spp[['bnt']][[1]]), 
                data.frame(stats3Spp[['ats']][[1]])) %>%
          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[1]])))

@@

multiplot(p1, p2, p3, p4, p5, cols=2)

>>>>

#data for running the simulation
simData <- list(
  nReps = 100, #num of mcmc iterations to grab
  numInd = 500 , # number of individual to simulate
  nOccYOY = 3,
  nOccAdult = 7,
  riverIndex = 1, #Levels: west brook < wb jimmy < wb mitchell < wb obear
  minSD = -1.5, #range and step for independent variable values in the sim
  maxSD = 1.5, 
  step = 1.5
)
simData$nOcc <- simData$nOccYOY + simData$nOccAdult
simData$indVarSeq = seq(simData$minSD,simData$maxSD,simData$step)

stats3Spp <- grStats3Spp <- anov <- elapsed <- lm <- relImp <- list()
spp <- c('bkt','bnt') #,'ats')

@@

  startTime <- Sys.time()
  sizeStats <- sizeStats2 <- grStats <- grStats2 <- NULL
  #loop over conditions
  for(testRow in indVars$rowNum){
    project <- projectSizes(m,simData,testRow)

    sizeMat <- project$sizeMat
    grMat <- project$grMat

    sizeStats1 <- summarizeLens(sizeMat,testRow)
    sizeStats <- rbind(sizeStats,sizeStats1[[1]]) #means over individuals (grouped by iter, occ)
    sizeStats2 <- rbind(sizeStats2,sizeStats1[[2]]) #means by occ of means over individuals (grouped by occ)

    grStats1 <- summarizeGRs(grMat,testRow)
    grStats <- rbind(grStats,grStats1[[1]]) #means over individuals (grouped by iter, occ)
    grStats2 <- rbind(grStats2,grStats1[[2]]) #means by occ of means over individuals (grouped by occ)
  }
  endTime <- Sys.time()
  (elapsed[[speciesForProj]] <- endTime - startTime)

  stats3Spp[[speciesForProj]] <- list( sizeStats,sizeStats2 )
  grStats3Spp[[speciesForProj]] <- list( grStats,grStats2 )

  # lm[[speciesForProj]] <- lm( lenMean ~ temp + flow + bkt + bnt + ats + temp * flow + temp^2 + flow^2 + bnt*bkt, data = sizeStats %>% filter(occ == (simData$nOcc)))
  # 
  # relImp[[speciesForProj]] <- calc.relimp(lm[[speciesForProj]], type = c("lmg"), rela = TRUE)
  #   
  # anov[[speciesForProj]] <- anova( lm[[speciesForProj]] )

@@

#projOut <- list(stats3Spp, lm, relImp, anov, elapsed, simData)
save( stats3Spp, grStats3Spp, elapsed, simData, file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))

# if not re-running the sim
# load( file = 'D:/projects/linkedModels/data/out/projectionOut.RData')
# load( file = paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))
# spp <- c('bkt','bnt','ats')

# raw sim data figs - size
ggplot(stats3Spp[['bkt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0), aes(as.numeric(occ),lenMean)) +
  geom_jitter(aes(color = factor(ats))) +
  #geom_smooth(aes(color = factor(temp), linetype = factor(flow)))+#(bnt + 2)/4 )) +
  geom_smooth()+#(bnt + 2)/4 )) +
  geom_smooth(color = 'green', data = stats3Spp[['bnt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0)) +
  facet_grid(temp ~ flow)

########################
# raw sim data figs - gr
ggplot(grStats3Spp[['bkt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0), aes(as.numeric(occ),grMean)) +
  geom_jitter(aes(color = factor(ats)), width = 0.2, size = 0.5) +
  #geom_smooth(aes(color = factor(temp), linetype = factor(flow)))+#(bnt + 2)/4 )) +
  #geom_smooth()+#(bnt + 2)/4 )) +
  geom_jitter(color = 'darkblue', width = 0.1, size = 0.5, data = grStats3Spp[['bnt']][[1]] %>% filter(ats == 0, bkt == 0, bnt == 0)) +
  facet_grid(temp ~ flow)

```{r RI across occ - use this for paper GROWTH RATE}

# relative proportion stats with occ in the lm 
grStats3Spp[['bkt']][[1]]$season <- as.factor(c(3,4,1,2,3,4,1,2,3,4))
grStats3Spp[['bkt']][[1]]$temp2 <- grStats3Spp[['bkt']][[1]]$temp^2
grStats3Spp[['bkt']][[1]]$flow2 <- grStats3Spp[['bkt']][[1]]$flow^2

ageForRI <-  'yoy' #'yoy' or 'adult'
occs <- if (ageForRI == 'yoy') 1:2 else 3:10
indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
indepVars <- c('temp', 'flow', 'temp:flow', 'bkt', 'bnt', 'ats', 'bkt:bnt')
rIBKTBNT <- NULL
# loop over occs
for(rep in 1:simData$nReps){

  print(rep)

  datOccBKT <- grStats3Spp[['bkt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
  lmAllBKT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKT) 
  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)

  datOccBNT <- grStats3Spp[['bnt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
  lmAllBNT <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNT)
  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)

  lmgBKT <- relImpAllBKT$lmg[(names(relImpAllBKT$lmg) %in% indepVars)]
  rBKT <- lmgBKT / sum(lmgBKT)

  lmgBNT <- relImpAllBNT$lmg[(names(relImpAllBNT$lmg) %in% indepVars)]
  rBNT <- lmgBNT / sum(lmgBNT)

  rIBKTBNT <- rbind(rIBKTBNT, data.frame(cbind(rBKT,rBNT)) %>% 
                      rownames_to_column() %>% 
                      gather(key = rowname) %>% 
                      mutate(var = rep(1:length(indepVars),2),
                             varText = rep(names(rBKT),2),
                             iter = rep)
                    )
}

rIBKTBNTMeans <- rIBKTBNT %>%
  group_by(rowname, var) %>%
  summarise(rIMean = mean(value),
            rISd = sd(value),
            rIUpperCI = quantile(value, 0.95))

dodge <- position_dodge(width=0.9)
ggplot(rIBKTBNTMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
  geom_col(position=dodge) +
  scale_x_discrete('Parameter',
                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
  scale_fill_grey() +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  geom_hline(yintercept = 0) +
  theme( legend.position = 'none')

ggsave(paste0('figures/3Spp_WB/relImpOccMeanModWOcc_GR',simData$nReps,'_',ageForRI,'.png'), width = 9, height = 7, units='in')

# uses 42 G - does not run
#lmAll <- lm( lenMean ~ (temp + flow +  temp^2 + flow^2 + bkt + bnt + ats )*occ + temp * flow + bnt * bkt, data = stats3Spp[['bkt']][[1]] %>%               filter(iter %in% 1) )

rIBKTBNT %>%
  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
  group_by(rowname,isEnvVar) %>%
  summarize(meanMean = mean(value),
            sumMean = sum(value),
            sdMean = sd(value))
# 25 reps
#   rowname isEnvVar meanMean sumMean sdMean
#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
# 1 rBKT           0   0.0664   0.265  0.105
# 2 rBKT           1   0.245    0.735  0.249
# 3 rBNT           0   0.147    0.588  0.104
# 4 rBNT           1   0.137    0.412  0.158

# 100 reps
#   rowname isEnvVar meanMean sumMean sdMean
#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
# 1 rBKT           0   0.0676    27.0 0.0914
# 2 rBKT           1   0.243     73.0 0.200 
# 3 rBNT           0   0.146     58.2 0.0922
# 4 rBNT           1   0.139     41.8 0.131

# ratio of env/(env+spp) means
.243/(.243 + .0676) # bkt 0.7823567
.139/(.139 + .146) # bnt 0.4877193

.782/.488 # 1.60
##############################################################
############################################################

# projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
load(paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))

#spp <- c('bkt','bnt','ats')
# scenarios
# Plot subsets of the simulations
#means for each iter
stats1 <- rbind(data.frame(grStats3Spp[['bkt']][[1]]), 
                data.frame(grStats3Spp[['bnt']][[1]]), 
                data.frame(grStats3Spp[['ats']][[1]])) %>%
          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[1]])))

#means for each occ
stats2 <- rbind(data.frame(grStats3Spp[['bkt']][[2]]), 
                data.frame(grStats3Spp[['bnt']][[2]]), 
                data.frame(grStats3Spp[['ats']][[2]])) %>%
          mutate(spp = rep(spp, each = nrow(grStats3Spp[['bkt']][[2]])))

ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
  geom_point(aes(color = spp) ) +
  geom_line( aes(color = spp) ) +
  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0) ) +
  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 1.5, flow == 0, bkt == 0, bnt == 0, ats == 0), linetype = 2 )

ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
  geom_point(aes(color = spp) ) +
  geom_line( aes(color = spp) ) +
  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0) ) +
  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 1.5, bkt == 0, bnt == 0, ats == 0), linetype = 2 )

ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, ats == 0), aes(occ,grMeanMean, group = spp)) +
  geom_point(aes(color = spp) ) +
  geom_line( aes(color = spp) ) +
  geom_point(aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0) ) +
  geom_line( aes(color = spp), data = stats2 %>% filter(temp == 0, flow == 0, bkt == 1.5, bnt == 0, ats == 0), linetype = 2 )

# trajectories across indep var values for different combinations. Trying to relate to relImp results
#temp
p1 <- ggplot( stats2 %>% filter(flow == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(temp))) +
  geom_line(aes(color = factor(temp))) +
  geom_point(aes(color = factor(temp))) +
  facet_wrap(~spp)

#flow
p2 <- ggplot( stats2 %>% filter(temp == 0, bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
  geom_line(aes(color = factor(flow))) +
  geom_point(aes(color = factor(flow))) +
  facet_wrap(~spp)

#bkt
p3 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bkt))) +
  geom_line(aes(color = factor(bkt))) +
  geom_point(aes(color = factor(bkt))) +
  facet_wrap(~spp)

#bnt
p4 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
  geom_line(aes(color = factor(bnt))) +
  geom_point(aes(color = factor(bnt))) +
  facet_wrap(~spp)

#ats
p5 <- ggplot( stats2 %>% filter(temp == 0, flow == 0, bkt == 0, bnt == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(ats))) +
  geom_line(aes(color = factor(ats))) +
  geom_point(aes(color = factor(ats))) +
  facet_wrap(~spp)

multiplot(p1, p2, p3, p4, p5, cols=2) # multiplot function is below

#temp*flow
ggplot( stats2 %>% filter(bkt == 0, bnt == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(flow))) +
  geom_line(aes(color = factor(flow))) +
  geom_point(aes(color = factor(flow))) +
  facet_grid(temp~spp)

#bkt*bnt
ggplot( stats2 %>% filter(temp == 0, flow == 0, ats == 0, spp %in% c('bkt','bnt')), aes(occ,grMeanMean, group = factor(bnt))) +
  geom_line(aes(color = factor(bnt))) +
  geom_point(aes(color = factor(bnt))) +
  facet_grid(bkt~spp)

```{r RI by occ - not used for paper GROWTH}

# make figures of relative importance for each sampling occasion
rIAll <- cAll <- NULL
for( occSelected in 1:(simData$nOcc - 1)){
  print(occSelected)
  lmAll <- ggRIAll <- relImpAll <- coefsAll <- list()

      lmAll[[spp1]] <- lm( grMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt, data = grStats3Spp[[spp1]][[1]] %>% filter(occ == occSelected, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals))
  #stats3Spp[[spp1]][[1]] %>% filter(occ == occSelected)

  # make bar chart of relative importance of each variable for each spp
  rI <- cbind(data.frame(bktRI = relImpAll[['bkt']]$lmg), 
              data.frame(bntRI = relImpAll[['bnt']]$lmg)) %>%
        rownames_to_column() %>% 
        gather(key=rowname) %>% 
        mutate(var = rep(1:length(relImpAll[['bkt']]$lmg),length(spp)),
               occ = occSelected,
               season = simData$seasons[occSelected])

  rIAll$age <- ifelse(rIAll$occ %in% 1:2, 0, ifelse(rIAll$occ %in% 3:6, 1, 2))

  ggplot(rI, aes(factor(var),value, fill = factor(rowname, levels = c('bktRI','bntRI'), ordered = TRUE))) +
    geom_col(position='dodge') +
    scale_x_discrete('Parameter',
                     labels = c('1' = 'Temp','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
    scale_fill_grey() +
    scale_y_continuous('Relative proportion of variance explained') +
    ggtitle(paste0("occ = ",occSelected,"  Season = ",simData$seasons[occSelected])) +
    theme_publication() +
    theme( legend.position = 'none')

  # coefficients
  coefs <- cbind(data.frame(bktC = coefsAll[['bkt']]), 
                 data.frame(bntC = coefsAll[['bnt']])) %>%
        rownames_to_column() %>% 
        gather(key=rowname) %>% 
        mutate(var = rep(1:length(coefsAll[['bkt']]),length(spp)),
               occ = occSelected,
               season = simData$seasons[occSelected])

ggplot(rIAll %>% filter(rowname %in% c('bktRI','bntRI')), aes((occ), value, color = factor(rowname))) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = 2.5) +
  scale_x_continuous('Sampling occasion',
                    breaks = 1:9,
                    labels = c('Autumn','Winter','Spring','Summer', 'Autumn','Winter','Spring','Summer', 'Autumn')
                    ) +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  theme(axis.text.x  = element_text(angle=90, vjust=0.25, size=10)) +
  facet_wrap(~ var, labeller=labeller(var = labels))

ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR.png'), width = 11, height = 9, units='in')

rIAllMinus <- rIAll %>% mutate(value2 = ifelse(rowname == 'bktRI',value * -1, value))
labelsSeason <- c('1'='Autumn','2'='Winter','3'='Spring','4'='Summer','5'='Autumn','6'='Winter','7'='Spring','8'='Summer','9'='Autumn')
labelsSeason2 <- c('1'='Spring','2'='Summer','3'='Autumn','4'='Winter')

ggplot(rIAllMinus, aes(var, y = value2, fill = rowname)) +
  geom_col() +
  coord_flip() +
  scale_x_reverse('Variable', 
                     breaks = 1:7,
                     labels = c('Temp', 'Flow', 'Bkt', 'Bnt','Ats','Temp*Flow',  "Bkt*Bnt")) +
  scale_y_continuous('Relative proportion of variance explained',
                     breaks = c(-1.0, -0.5, 0.0, 0.5),
                     labels = c('1.0', '0.5', '0.0', '0.5')) +
  theme_publication() +
  scale_fill_grey(start = 0.15, end = 0.75) +
  facet_grid(season ~ age, labeller=labeller(season = labelsSeason2))

ggsave(paste0('figures/3Spp_WB/relImpOccAll_GR_HorizBars.png'), width = 11, height = 9, units='in')

```{r RI by occ - not used for paper SIZE}

@@

```{r RI across occ - use this for paper SIZE}

# relative proportion stats with occ in the lm 
stats3Spp[['bkt']][[1]]$season <- as.factor(c(3,4,1,2,3,4,1,2,3,4))
stats3Spp[['bkt']][[1]]$temp2 <- stats3Spp[['bkt']][[1]]$temp^2
stats3Spp[['bkt']][[1]]$flow2 <- stats3Spp[['bkt']][[1]]$flow^2

ageForRI <-  'adult' #'yoy' or 'adult'
occs <- if (ageForRI == 'yoy') 1:3 else 4:10
indepVarVals <- c(-1.5,0,1.5) # make sure symetrical around 0
rIBKTBNT <- NULL
# loop over occs
for(rep in 1:simData$nReps){

  print(rep)

  datOccBKT <- stats3Spp[['bkt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
  lmAllBKT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBKT) 
  relImpAllBKT <- calc.relimp(lmAllBKT, type = c("lmg"), rela = TRUE)

  datOccBNT <- stats3Spp[['bnt']][[1]] %>% filter(iter == rep, occ %in% occs, temp %in% indepVarVals, flow %in% indepVarVals, bkt %in% indepVarVals, bnt %in% indepVarVals, ats %in% indepVarVals)
  lmAllBNT <- lm( lenMean ~ temp + flow + temp * flow + temp^2 + flow^2 + bkt + bnt + ats + bnt * bkt + occ, data = datOccBNT)
  relImpAllBNT <- calc.relimp(lmAllBNT, type = c("lmg"), rela = TRUE)

  rBKT <- relImpAllBKT$lmg[2:8] / sum(relImpAllBKT$lmg[2:8]) 
  rBNT <- relImpAllBNT$lmg[2:8] / sum(relImpAllBNT$lmg[2:8])

  rIBKTBNT <- rbind(rIBKTBNT, data.frame(cbind(rBKT,rBNT)) %>% 
                      rownames_to_column() %>% 
                      gather(key = rowname) %>% 
                      mutate(var = rep(1:7,2),
                             varText = rep(names(rBKT),2),
                             iter = rep)
                    )

rIBKTBNTMeans <- rIBKTBNT %>%
  group_by(rowname, var) %>%
  summarise(rIMean = mean(value),
            rISd = sd(value),
            rIUpperCI = quantile(value, 0.95))

dodge <- position_dodge(width=0.9)
ggplot(rIBKTBNTMeans, aes(factor(var),rIMean, fill = factor(rowname, levels = c('rBKT','rBNT'), ordered = TRUE))) +
  geom_errorbar(aes(ymin = rIMean - 0.001, ymax = rIUpperCI), width = 0.25, position=dodge) +
  geom_col(position=dodge) +
  scale_x_discrete('Parameter',
                   labels = c('1' = 'Temperature','2' = 'Flow','3' = 'Bkt','4' = 'Bnt','5' = 'Ats','6' = 'Temp*Flow', '7' = "Bkt*Bnt")) +
  scale_fill_grey() +
  scale_y_continuous('Relative proportion of variance explained') +
  theme_publication() +
  geom_hline(yintercept = 0) +
  theme( legend.position = 'none')

ggsave(paste0('figures/3Spp_WB/relImpOccMeanModWOcc_Size',simData$nReps,'_',ageForRI,'.png'), width = 9, height = 7, units='in')

# uses 42 G - does not run
#lmAll <- lm( lenMean ~ (temp + flow +  temp^2 + flow^2 + bkt + bnt + ats )*occ + temp * flow + bnt * bkt, data = stats3Spp[['bkt']][[1]] %>%               filter(iter %in% 1) )

rIBKTBNT %>%
  mutate(isEnvVar = ifelse(var %in% c(1,2,6), 1,0)) %>%
  group_by(rowname,isEnvVar) %>%
  summarize(meanMean = mean(value),
            sumMean = sum(value),
            sdMean = sd(value))
# 25 reps
#   rowname isEnvVar meanMean sumMean sdMean
#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
# 1 rBKT           0   0.0664   0.265  0.105
# 2 rBKT           1   0.245    0.735  0.249
# 3 rBNT           0   0.147    0.588  0.104
# 4 rBNT           1   0.137    0.412  0.158

# 100 reps
#   rowname isEnvVar meanMean sumMean sdMean
#   <chr>      <dbl>    <dbl>   <dbl>  <dbl>
# 1 rBKT           0   0.0676    27.0 0.0914
# 2 rBKT           1   0.243     73.0 0.200 
# 3 rBNT           0   0.146     58.2 0.0922
# 4 rBNT           1   0.139     41.8 0.131

# ratio of env/(env+spp) means
.243/(.243 + .0676) # bkt 0.7823567
.139/(.139 + .146) # bnt 0.4877193

.782/.488 # 1.60
##############################################################
############################################################

# projOut <- list(stats3Spp, lm, relImp, anov, elapsed)
load(paste0('D:/projects/linkedModels/data/out/projectionOut_N',simData$nReps,'.RData'))

spp <- c('bkt','bnt','ats')
# scenarios
# Plot subsets of the simulations
#means for each iter
stats1 <- rbind(data.frame(stats3Spp[['bkt']][[1]]), 
                data.frame(stats3Spp[['bnt']][[1]]), 
                data.frame(stats3Spp[['ats']][[1]])) %>%
          mutate(spp = rep(spp, each = nrow(stats3Spp[['bkt']][[1]])))

@@

multiplot(p1, p2, p3, p4, p5, cols=2) # multiplot function is below
